---
title: "Hw5"
author: 'IRENE MARTINEZ MORATA (UNI: im2557)'
date: "11/18/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(ggplot2)
library(readxl)
library(purrr)

getwd()
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1


```{r }

df_homicides =
  read_csv("homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when (
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )) %>% 
  relocate(city_state) 

```
This data contains information about homicides in 50 large U.S. cities. It includes `r nrow(df_homicides)` observations for the following variables: `r colnames(df_homicides)`

Next, focusing on Baltimore, MD (using prop.test), the proportion of homicides that are unresolved is 0.645, with a 95% confidence interval of (0.63, 0.66)

```{r }
baltimore_df =
  df_homicides %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary =
  baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"), 
    n = n()
  )

baltimore_test = 
  prop.test(
  x= baltimore_summary %>% pull(unsolved),
  n=baltimore_summary %>%  pull(n)
)

baltimore_test %>% 
  broom::tidy()
```

To iterate this estimation to all cities in the dataset, we write a function.


```{r }
prop_test_function = function (city_df) {

city_summary =
  df_homicides %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"), 
    n = n()
    )

city_test = 
  prop.test(
  x = city_summary %>% pull(unsolved),
  n = city_summary %>%  pull(n))

return(city_test)

}



df_homicides %>% 
filter(city_state == "AlbuquerueNM") %>% 
prop_test_function()

```

Now let's iterate across all cities

```{r }
results_df =
  df_homicides %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))

```

plot showing estimates and confidence intervals

```{r }
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x= city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin =conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust=0.5, hjust=1))


```




```{r }
df_homicides %>% 
  group_by(city_state) %>% 
  summarise(
    unsolved= sum(resolution =="unsolved"),
    n = n()
  ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))


```



##Problem 2

Importing the data
```{r }
problem2 = tibble (
  files = list.files("./data/")
  )

read_data <- function(file_name) {
  
  read_csv(paste0("./data/", file_name))
  
}

study_data = 
  problem2 %>% 
  mutate(
    problem2 = map(files[[1]], read_data))
```
Now, let´s tidy the data
- Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
```{r}
study_data_good = 
  study_data %>% 
  unnest(problem2) %>% 
  separate(files, into = c("study_group", "subject_id"), sep = "\\_") %>% 
  mutate(
    subject_id = str_replace(subject_id, "\\.csv", ""),
    study_group = recode(study_group, con = "Control", exp = "Experimental")) %>% 
   gather(key = week, value = observation, week_1:week_8) 
study_data_good
```

Spaghetti plot showing observations on each subject over time, and comment on differences between group

```{r}
study_data_good %>% 
  ggplot(aes(x = week, y = observation, color = subject_id, group = subject_id)) + 
  geom_line() +
  facet_grid(~study_group) +
  labs(
    title = "Observations during 8 weeks", 
    x = "Week", 
    y = "Observation", 
    color = "Participant")
   
```
The observations we

## Problem 3:


```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

dat <- vector("list", length = ncol(iris_with_missing))


na_replace <- function(x) {
  if (is.numeric(x)) {
    replace_na(x, mean(x, na.rm = TRUE))
    
  }  else if (is.character(x)) {
    replace_na(x, "virginica")
  }
}


data <- map(iris_with_missing, na_replace)
```



